Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-07-30 paper/main.tex
check in our notes from the call

\item[RQ4]{FIXME predicates?}

@@

@@

@@

prereq: define defect category. This could be either the raw python
exception name or it could be clusters that we have manually created.

@@

PLOT Y Axis: Leave-One-In Accuracy (normalized per X axis point)

@@

>>>>

\item[RQ4]{Is our algorithm accurate on heterogeneous sets of programs?}

@@

Ranjit: ``our algorithms'' --- ``purely syntactic vs. with types'' 
--- ``with or without slicing'' as extra ``bars''

@@

TODO: what about turning on/off slicing?

TODO: what about turning on/off types? (is that separate from slicing?)

TODO: do ANOVA or ReliefF

@@

prereq: define defect category. This could be either the raw python
exception name or it could be clusters that we have manually created. 
Ranjit notes: result could be ``we need everything for everything'', at
which point this is useless and should be skipped. Per Ben's exam: may find
that for different categories of errors we should use different ML
classifiers.

@@

PLOT Y Axis: Leave-One-In Accuracy (normalized per X axis point)
Ranjit notes: on smaller subsets we could rebuild the classifier each time.
Wes notes that if we do, it takes us longer. If we re-use the monolithic
model we can do this very quickly.

@@

\subsection{RQ 4 --- Diversity of Programs}

In Nate there were 20 different functions. All the programs were doing the
same 20 functions.

Here, people are doing anything they want. Random stuff going on over here.

We want to show that we get high accuracy *over a heterogenous set of
programs*. Leon?

prereq: cluster the programs based on similarity. Using agglomerative
clustering plus python edit distance. How good the performance will be?
right now it creates a clustering tree. binary tree, based on min distance. 
can give it a threshhold for distance (elements w/in a group). don't forget
to rename all variables to X, perhaps normalize (edit distance size).

leon: could also cluster by inconsistency coefficient

PLOT Type: line graph (standard plot)

PLOT X AXIS: clustering distance parameter

PLOT Y AXIS: number of different clusters found

PLOT LINES: line 1 is ``Nate programs'', line 2 is ``25\%, at random, of our dataset''

Goal: show that ``no matter how you decide program differences'', our
dataset is always more diverse/heterogeneous than is previous work. So our
success is amazing.

\subsection{RQ 5 --- Wishlist: Partitioning Kinds of Errors}

Can we partition the kinds of errors that people make? What are common
misconceptions? Do these correspond to paths of decision trees.

If we don't get to the source-sink thing, it could go here.

I don't think we have time, in this paper, to actually implement a
two-level machine learning.
